Handovers - SIPHER 7 Equivalent Income

### 2023-06-12 minos/validation/handovers_S7.Rmd
Setting factor levels of S7_neighbourhood_safety to ensure predicted values match the correct levels. Also expanding the handovers_S7 notebook

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
source('Minos/minos/utils_datain.R')
source('Minos/minos/utils_validation_vis.R')
```

@@

out.path <- 'Minos/output/SIPHER7/'
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

@@

## Housing Quality

```{r}
# first figure out how to plot final_US
# start with hh_income
raw <- raw.dat %>% 
  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
  group_by(time) %>%
  summarise(housing_quality = mean(S7_housing_quality, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base <- base.dat %>%
  dplyr::select(pidp, time, S7_housing_quality, weight) %>%
  group_by(time) %>%
  summarise(housing_quality = mean(S7_housing_quality)) %>%
  mutate(source = 'baseline_output')

# merge before plot
housing_quality <- rbind(raw, base)

# Now plot
ggplot(data = housing_quality, mapping = aes(x = time, y = housing_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Income')
```

TODO: Make these ordinal plots as handovers (might just need to change cv to baseline?)

```{r}
hous.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'S7_housing_quality')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'housing_quality',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

spaghetti_plot(spag, 'S7_housing_quality',
               save = TRUE,
               save.path = save.path)

>>>>

require(tidyverse)
require(ggplot2)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

@@

#out.path <- 'Minos/output/SIPHER7/'
out.path <- here::here('output', 'SIPHER7/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

spaghetti_plot(base.ei, 'equivalent_income')

@@

## S7 Housing Quality

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_housing_quality')

housing <- prepped.list$var
housing.norm <- prepped.list$norm

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = S7_housing_quality, colour = S7_housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Housing Quality', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=S7_housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Housing Quality') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'S7_housing_quality.png',
       plot = last_plot(),
       path = save.path)

rm(prepped.list, housing, housing.norm)
```

```{r}
hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_housing_quality')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

spaghetti_plot(spag, 'S7_housing_quality',
               save = FALSE,
               save.path = save.path)

## S7 Neighbourhood Safety

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_neighbourhood_safety')

nh_safety <- prepped.list$var
nh_safety.norm <- prepped.list$norm

# Now plot
ggplot(data = nh_safety, mapping = aes(x = time, y = n, group = S7_neighbourhood_safety, colour = S7_neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Neighbourhood Safety', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = nh_safety.norm, mapping = aes(x = time, y = prct, fill=S7_neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Neighbourhood Safety') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'S7_neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)

rm(prepped.list, nh_safety, nh_safety.norm)
```

```{r}
hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_neighbourhood_safety')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = FALSE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = TRUE,
               save.path = save.path)
